### 2019-07-03 2-Chapters/4-Chapter/IEEE_WCNC__2019__Paper__BMBM.git/IEEE_WCNC__2019__Paper__BMBM.tex
Done for 2day

In order to assess the proposed approximation, we suppose a unique channel where all the devices follow the same contention Markov process.
We simulate an ALOHA protocol with a maximum number of retransmissions $\mathrm{MaxBackOff}=10$, a maximum back-off interval $m=10$, and a transmission probability $p=10^{-3}$.
%
In Figure~\ref{fig:43:Approximation_m10}, we show the collision probabilities for different number of devices $N$ (from $N=50$ to $N=400$), for both $p_{c}$ and $p_{c1}$.
%
We can verify that our approximation is very precise for lower values $p_{c1} \leq 30 \%$ (\ie, red and orange curves are quite close).
Moreover, a significant gap between $p_{c1}$ and $p_c$,
of up-to $10\%$, can be observed,
which suggests us to resort to MAB algorithms for the channel selection for both the first transmission and next retransmissions.

\begin{figure}[htp!]  % [htbp]
	\centering
	% \includegraphics[width=0.65\linewidth]{Approximation_m10.eps}
	\includegraphics[width=0.60\linewidth]{Approximation_m10-eps-converted-to.pdf}
	\caption[Proposed approximation for the probability of collision at the second transmission.]{Proposed approximation for the probability of collision at the second transmission. It is more precise for smaller values of $N$.}
	\label{fig:43:Approximation_m10}
\end{figure}

>>>>

In order to assess the proposed approximation, we suppose a unique channel where all the devices follow the same contention Markov process.
We simulate an ALOHA protocol with a maximum number of retransmissions $\mathrm{MaxBackOff}=10$, a maximum back-off interval $m=10$, and a transmission probability $p=10^{-3}$.
%
In Figure~\ref{fig:43:Approximation_m10}, we show the collision probabilities for different number of devices $N$ (from $N=50$ to $N=400$), for both $p_{c}$ and $p_{c1}$.
%
We can verify that our approximation is very precise for lower values $p_{c1} \leq 30 \%$ (\ie, \textcolor{red}{red} and \textcolor{gold}{orange} curves are quite close).
Moreover, a significant gap between $p_{c1}$ and $p_c$,
of up-to $10\%$, can be observed,
which suggests us to resort to MAB algorithms for the channel selection for both the first transmission and next retransmissions.

\begin{figure}[htp!]  % [htbp]
	\centering
	% \includegraphics[width=0.65\linewidth]{Approximation_m10.eps}
	\includegraphics[width=0.60\linewidth]{Approximation_m10-eps-converted-to.pdf}
	\caption[Our approximation for the probability of collision at the second transmission.]{\textcolor{red}{Our approximation (in red)} of \textcolor{gold}{$p_{c1}$ (in orange)}, probability of collision at the second transmission, is more precise for smaller $N$. We also include \textcolor{blue}{$p_{c}$ (in blue)}.}
	\label{fig:43:Approximation_m10}
\end{figure}

### 2019-07-03 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
Done for 2day

%
% Regular plots of centralized regrets
%
\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{0.49\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K3_M2_T5000_N1000__4_algos/all_HistogramsRegret____env1-1_5016720151160452442.pdf}
  % \end{subfigure}
  % % ~
  % \begin{subfigure}[!h]{0.49\textwidth}
  %   \includegraphics[width=1.10\textwidth]{MP__K3_M3_T5000_N1000__4_algos/all_HistogramsRegret____env1-1_1035303196230283176.pdf}
  % \end{subfigure}
  \caption[Failure case of \Selfish.]{Regret for $M=2$ players, $K=3$ arms, horizon $T=5000$, $1000$ repetitions and $\boldsymbol{\mu} = [0.1, 0.5, 0.9]$. Axis $x$ is for regret (different scale for each part), and the \textcolor{darkgreen}{green} curve for \Selfish{} shows a small probability of having a linear regret ($17$ cases of $R_T \geq T$, out of $1000$). The regret for the three other algorithms is very small for this problem, always smaller than $100$ here.}
  \label{fig:5:selfish_fail1}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

@@

\begin{figure}[!b]
  \centering
  % \begin{subfigure}[!h]{0.85\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{0.85\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_HistogramsRegret____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  \caption[Regret for $M=6$ players for $K=9$ arms, horizon $T=5000$, for $1000$ repetitions on a fixed problem.]{Regret (in log-log scale), for $M=6$ players for $K=9$ arms, horizon $T=5000$, for $1000$ repetitions on problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$. \RandTopM{} (\textcolor{gold}{yellow} curve) outperforms \Selfish{} (\textcolor{darkgreen}{green}), both clearly outperform \rhoRand. The regret of \MCTopM{} is logarithmic, empirically with the same slope as the lower bound. The $x$ axis on the regret histograms have different scale for each algorithm.}
  \label{fig:5:MP__K9_M6_T10000_N1000__4_algos}
\end{figure}

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_2643359116089264295.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
  %   \includegraphics[width=1.00\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T10000_N200__4_algos/all_RegretCentralized_loglog____env1-1_2306423191427933958.pdf}
  % \end{subfigure}
  \caption[Regret for $M=2$ and $9$ players for $K=9$ arms, horizon $T=5000$, for a fixed problem.]{Regret (in log-log scale), for $M=2$ and $9$ players for $K=9$ arms, horizon $T=5000$, for problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$] for problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$. In different settings, \RandTopM{} (\textcolor{gold}{yellow} curve) and \Selfish{} (\textcolor{darkgreen}{green}) can outperform each other, and always outperform \rhoRand. \MCTopM{} is always among the best algorithms, and for $M$ not too small, its regret seems logarithmic with a constant matching the lower bound.}
  \label{fig:5:MP__K9_M2-6-9_T10000_N200__4_algos}
\end{figure}

@@

%
% Regular plots of centralized regrets
%
\begin{figure}[!t]
  % \centering
  % \begin{subfigure}[!h]{0.49\textwidth}
  %   \includegraphics[width=1.00\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_RegretCentralized____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  % % ~
  % \begin{subfigure}[!h]{0.49\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T5000_N500__4_algos/all_RegretCentralized____env1-1_8318947830261751207.pdf}
  % \end{subfigure}
  \caption[Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled.]{Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \rhoRand{} (top \textcolor{blue}{blue} curve) is outperformed by the other algorithms (and the gain increases with $M$). \MCTopM{} (bottom \textcolor{gold}{yellow}) outperforms all the other algorithms in most cases.}
  % \label{fig:5:MP__K9_M2-6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  \label{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

@@

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_RegretCentralized____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  % ~
  \vspace{15pt}%  FIXME?
  % \begin{subfigure}[!h]{1.00\textwidth}
      % \includegraphics[width=1.00\textwidth]{MP__K9_M6_T5000_N500__4_algos/all_RegretCentralized____env1-1_8318947830261751207.pdf}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_HistogramsRegret____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  \caption[Regret for $M=2$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled.]{Regret for $M=2$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \rhoRand{} (top \textcolor{blue}{blue}) is outperformed by the other algorithms (and the gain increases when $M$ increases), which all perform similarly in such configurations. Note that the (small) tail of the histograms come from complicated problems $\boldsymbol{\mu}$ and not failure cases.}
  \label{fig:5:MP__K9_M2_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T5000_N500__4_algos/all_RegretCentralized____env1-1_3892966382091165662.pdf}
  % \end{subfigure}
  % ~
  \vspace{20pt}%  FIXME?
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T5000_N500__4_algos/all_HistogramsRegret____env1-1_3892966382091165662.pdf}
  % \end{subfigure}
  \caption[Regret for $M=K=9$, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled.]{Regret for $M=K=9$, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. This extreme case $M=K$ shows the drastic difference of behavior between \RandTopM{} and \MCTopM, having constant regret, and \rhoRand{} and \Selfish, having large regret.}
  \label{fig:5:MP__K9_M9_T5000_N500__4_algos__all_HistogramsRegret}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

>>>>

%
% Regular plots of centralized regrets
%
\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{0.49\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K3_M2_T5000_N1000__4_algos/all_HistogramsRegret____env1-1_5016720151160452442.pdf}
  % \end{subfigure}
  % % ~
  % \begin{subfigure}[!h]{0.49\textwidth}
  %   \includegraphics[width=1.10\textwidth]{MP__K3_M3_T5000_N1000__4_algos/all_HistogramsRegret____env1-1_1035303196230283176.pdf}
  % \end{subfigure}
  \caption[Failure case of \Selfish.]{Regret for $M=2$ players, $K=3$ arms, horizon $T=5000$, $1000$ repetitions and $\boldsymbol{\mu} = [0.1, 0.5, 0.9]$. Axis $x$ is for regret (different scale for each part), and the \textcolor{darkgreen}{green curve for \Selfish} shows a small probability of having a linear regret ($17$ cases of $R_T \geq T$, out of $1000$). The regret for the three other algorithms is very small for this problem, always smaller than $100$ here.}
  \label{fig:5:selfish_fail1}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

@@

\begin{figure}[!b]
  \centering
  % \begin{subfigure}[!h]{0.85\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{0.85\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_HistogramsRegret____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  \caption[Regret for $M=6$ players for $K=9$ arms, horizon $T=5000$, for $1000$ repetitions on a fixed problem.]{Regret (in log-log scale), for $M=6$ players for $K=9$ arms, horizon $T=5000$, for $1000$ repetitions on problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$. \textcolor{gold}{\RandTopM{} (in yellow)} outperforms \textcolor{darkgreen}{\Selfish{} (in green)}, both clearly outperform \rhoRand. The regret of \MCTopM{} is logarithmic, empirically with the same slope as the lower bound. The $x$ axis on the regret histograms have different scale for each algorithm.}
  \label{fig:5:MP__K9_M6_T10000_N1000__4_algos}
\end{figure}

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_2643359116089264295.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
  %   \includegraphics[width=1.00\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T10000_N200__4_algos/all_RegretCentralized_loglog____env1-1_2306423191427933958.pdf}
  % \end{subfigure}
  \caption[Regret for $M=2$ and $9$ players for $K=9$ arms, horizon $T=5000$, for a fixed problem.]{Regret (in log-log scale), for $M=2$ and $9$ players for $K=9$ arms, horizon $T=5000$, for problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$] for problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$. In different settings, \textcolor{gold}{\RandTopM{} (in yellow)} and \textcolor{darkgreen}{\Selfish{} (in green)} can outperform each other, and always outperform \rhoRand. \MCTopM{} is always among the best algorithms, and for $M$ not too small, its regret seems logarithmic with a constant matching the lower bound.}
  \label{fig:5:MP__K9_M2-6-9_T10000_N200__4_algos}
\end{figure}

@@

%
% Regular plots of centralized regrets
%
\begin{figure}[!t]
  % \centering
  % \begin{subfigure}[!h]{0.49\textwidth}
  %   \includegraphics[width=1.00\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_RegretCentralized____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  % % ~
  % \begin{subfigure}[!h]{0.49\textwidth}
    \includegraphics[width=0.95\textwidth]{MP__K9_M6_T5000_N500__4_algos/all_RegretCentralized____env1-1_8318947830261751207.pdf}
  % \end{subfigure}
  \caption[Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled.]{Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \textcolor{blue}{\rhoRand{} (top blue)} is outperformed by the other algorithms (and the gain increases with $M$). \textcolor{gold}{\MCTopM{} (bottom yellow)} outperforms all the other algorithms in most cases.}
  % \label{fig:5:MP__K9_M2-6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  \label{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

@@

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_RegretCentralized____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  % ~
  \vspace{15pt}%  FIXME?
  % \begin{subfigure}[!h]{1.00\textwidth}
      % \includegraphics[width=1.00\textwidth]{MP__K9_M6_T5000_N500__4_algos/all_RegretCentralized____env1-1_8318947830261751207.pdf}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_HistogramsRegret____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  \caption[Regret for $M=2$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled.]{Regret for $M=2$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \textcolor{blue}{\rhoRand{} (top blue)} is outperformed by the other algorithms (and the gain increases when $M$ increases), which all perform similarly in such configurations. Note that the (small) tail of the histograms come from complicated problems $\boldsymbol{\mu}$ and not failure cases.}
  \label{fig:5:MP__K9_M2_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T5000_N500__4_algos/all_RegretCentralized____env1-1_3892966382091165662.pdf}
  % \end{subfigure}
  % ~
  \vspace{20pt}%  FIXME?
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T5000_N500__4_algos/all_HistogramsRegret____env1-1_3892966382091165662.pdf}
  % \end{subfigure}
  \caption[Regret for $M=K=9$, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled.]{Regret for $M=K=9$, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. This extreme case $M=K$ shows the drastic difference of behavior between \textcolor{red}{\RandTopM{} (red)} and \textcolor{gold}{\MCTopM{} (yellow)}, with constant regret, and \textcolor{blue}{\rhoRand{} (blue)} and \textcolor{darkgreen}{\Selfish{} (green)}, with large regret.}
  \label{fig:5:MP__K9_M9_T5000_N500__4_algos__all_HistogramsRegret}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

### 2019-07-03 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits_appendix.tex
Done for 2day

We proved in Theorem~\ref{thm:5:BetterLowerBound} that the normalized regret, \ie, $R_T$ divided by
$\log T$, is asymptotically lower bounded by a constant $C_{\boldsymbol{\mu}, M}$
depending on the problem $\boldsymbol{\mu}$ and the number of players $M$, for any algorithm $\cA$ of a certain class.
%
We remind that if  $\cA=(\cA_1,\dots,\cA_M)$ is a strongly uniformly efficient \emph{decentralized} policy,
and if $\cA_j$ satisfies $\cI_{\bm{\mu},\bm{\lambda}}(\cA_j,T) = \smallO{\log(T)}$, then we obtained the following asymptotical result:
%
\begin{equation}
  \mathop{\lim\inf}\limits_{T \to +\infty} \frac{R_T^{\cA}(\boldsymbol{\mu}, M)}{\log T} \geq C_{\boldsymbol{\mu}, M}.
\end{equation}
%
For an example problem with $K = 9$ arms, we display below on the $x$ axis
the number of player, from $1$ player to $9$ players, and on the
$y$ axis the value of this constant $C_{\boldsymbol{\mu}, M}$, from the initial
theorem and from our theorem.
We chose a simple problem, with Bernoulli
distributed arms, with $\boldsymbol{\mu} = [0.1, 0.2, \dots, 0.9]$.
% (as used in some articles).
%
Figure~\ref{fig:5:CompLowerBounds} clearly shows that our improved lower bound is indeed larger than the initial one by \cite{Zhao10},
and both become uninformative when $M=K$ (\ie, it gives $R_T / \log(T) \geq 0$ which is obvious anyway).

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.95\textwidth]{Comparison_of_our_lowerbound_and_Anandkumar_2010__9_arms.pdf}
  \caption[Comparison of our lower bound against the one from \cite{Zhao10}.]{Comparison of our lower bound against the one from \cite{Zhao10}, on a simple problem with $9$ Bernoulli arms, of means $\boldsymbol{\mu} = [0.1, 0.2, \dots, 0.9]$, as a function of the number of players $M$.}
  \label{fig:5:CompLowerBounds}
\end{figure}

@@

The Figure~\ref{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6} below
shows the regret $R_T^{\cA}(\boldsymbol{\mu}, M)$
on the same example problem $\boldsymbol{\mu}$, with $K = 9$ arms and respectively $M = 6$, or $9$ players, for \Selfish-\klUCB.
%
It is just a simple way to check that the two lower bounds on the regret indeed appear as valid lower bounds empirically,
and are moreover lower bounds on the count of selections (\ref{eq:5:term1}, displayed in \textcolor{blue}{cyan}).
%
The lower bounds (in black) are $C(\boldsymbol{\mu}, M) \log t$, the dashed line
for the lower bound from \cite{Zhao10}, and the continuous line is our lower bound.
%
These plot show the regret (in red),
% the three lower bounds
% (centralized, \citeauthor{Anandkumar11}'s and our lower bounds, in black),
and the three terms \ref{eq:5:term1}, \ref{eq:5:term2}, \ref{eq:5:term3} in the decomposition of the regret.
As explained in Lemma~\ref{lem:5:DecompositionRegret}, term \ref{eq:5:term2} is not always non-negative.
For $M=9$ and \Selfish, \ref{eq:5:term3} is actually larger than the regret,
and term \ref{eq:5:term1} is zero, as well as the lower bounds.

%
% System regret and three terms
%
\begin{figure}[!h]
    \centering
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_2092905764868974160.pdf}
    % \end{subfigure}
    % ~
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_1699475021767911583.pdf}
    % \end{subfigure}
    \caption[Illustrating the decomposition of the multi-players regret with its three terms.]{The three terms \ref{eq:5:term1}, \ref{eq:5:term2}, \ref{eq:5:term3} of the multi-players regret, and lower bounds \eqref{eq:5:ourLowerBound} and \eqref{eq:5:Zhao10LowerBound} in \textbf{black}, for \Selfish-\klUCB: $M=6$ and $M=9$ players, $K=9$ arms, horizon $T=10000$ (for $1000$ runs).}
    \label{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6}
    % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

>>>>

We proved in Theorem~\ref{thm:5:BetterLowerBound} that the normalized regret, \ie, $R_T$ divided by
$\log T$, is asymptotically lower bounded by a constant $C_{\boldsymbol{\mu}, M}$
depending on the problem $\boldsymbol{\mu}$ and the number of players $M$, for any algorithm $\cA$ of a certain class.
%
We remind that if  $\cA=(\cA_1,\dots,\cA_M)$ is a strongly uniformly efficient \emph{decentralized} policy,
and if $\cA_j$ satisfies $\cI_{\bm{\mu},\bm{\lambda}}(\cA_j,T) = \smallO{\log(T)}$, then we obtained the following asymptotical result
$\mathop{\lim\inf}\limits_{T \to +\infty} \frac{R_T^{\cA}(\boldsymbol{\mu}, M)}{\log T} \geq C_{\boldsymbol{\mu}, M}$.
%
For an example problem with $K = 9$ arms, we display below on the $x$ axis
the number of player, from $1$ player to $9$ players, and on the
$y$ axis the value of this constant $C_{\boldsymbol{\mu}, M}$, from the initial
theorem and from our theorem.
We chose a simple problem, with Bernoulli
distributed arms, with $\boldsymbol{\mu} = [0.1, 0.2, \dots, 0.9]$.
% (as used in some articles).
%
Figure~\ref{fig:5:CompLowerBounds} clearly shows that our improved lower bound is indeed larger than the initial one by \cite{Zhao10},
and both become uninformative when $M=K$ (\ie, it gives $R_T / \log(T) \geq 0$ which is obvious anyway).

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.90\textwidth]{Comparison_of_our_lowerbound_and_Anandkumar_2010__9_arms.pdf}
  \caption[Comparison of our lower bound against the one from \cite{Zhao10}.]{Comparison of \textcolor{red}{our lower bound (in red)} against \textcolor{blue}{the one from \cite{Zhao10} (in blue)}, on a small problem with $9$ Bernoulli arms, of means $\boldsymbol{\mu} = [0.1, \dots, 0.9]$, as a function of the number of players $M$.}
  \label{fig:5:CompLowerBounds}
\end{figure}

@@

The Figure~\ref{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6} below
shows the regret $R_T^{\cA}(\boldsymbol{\mu}, M)$
on the same example problem $\boldsymbol{\mu}$, with $K = 9$ arms and respectively $M = 6$, or $9$ players, for \Selfish-\klUCB.
We considered $1000$ independent runs and plot the average regret.
%
It is just a simple way to check that the two lower bounds on the regret indeed appear as valid lower bounds empirically,
and are moreover lower bounds on the count of selections (\ref{eq:5:term1}, displayed in \textcolor{blue}{cyan}).
%
The lower bounds (in black) are $C(\boldsymbol{\mu}, M) \log t$, the dashed line
for the lower bound from \cite{Zhao10}, and the continuous line is our lower bound.
%
These plot show the regret (in red),
% the three lower bounds
% (centralized, \citeauthor{Anandkumar11}'s and our lower bounds, in black),
and the three terms \ref{eq:5:term1}, \ref{eq:5:term2}, \ref{eq:5:term3} in the decomposition of the regret.
As explained in Lemma~\ref{lem:5:DecompositionRegret}, term \ref{eq:5:term2} is not always non-negative.
For $M=9$ and \Selfish, \ref{eq:5:term3} is actually larger than the regret,
and term \ref{eq:5:term1} is zero, as well as the lower bounds.

%
% System regret and three terms
%
\begin{figure}[!h]
    \centering
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_2092905764868974160.pdf}
    % \end{subfigure}
    % ~
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_1699475021767911583.pdf}
    % \end{subfigure}
    \caption[Illustrating the decomposition of the multi-players regret with its three terms.]{The three terms \ref{eq:5:term1} (\textcolor{red}{in red}), \ref{eq:5:term2} (\textcolor{cyan}{in cyan}), \ref{eq:5:term3} (\textcolor{green}{in green}) of the multi-players regret, and lower bounds \eqref{eq:5:ourLowerBound} and \eqref{eq:5:Zhao10LowerBound} (\textbf{in black}), for \Selfish-\klUCB. Two cases for $M=6$ and $M=9$ players, $K=9$ arms, horizon $T=10000$.}
    \label{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6}
    % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

### 2019-07-03 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Done for 2day

Figure~\ref{fig:6:Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb1} above displays the locations of the successively detected change-points by four algorithms,
$1)$ \MklUCB,
$2)$ \CUSUMklUCB,
$3)$ \GLRklUCB{} with \emph{local restart},
$4)$ \GLRklUCB{} with \emph{global restart}.
In this ``easy'' problem, all algorithms correctly detect the important changes, except \CUSUM{} which detected a change on arm $1$ (in \textcolor{red}{red}) twice after the change-point located at $t=3000$.
The three other algorithms have a very small delay, for instance only $9$ samples from arm $0$ (in \textcolor{blue}{blue}) after its change at time $t=2000$ are enough for the \GLR{} test to detect a change.
Very small delays are possible only after having collected a lot of samples of the arm which changed, and for instance the same algorithm obtains a delay of $32$ samples from \textcolor{red}{arm $1$} for the next change at $t=3000$, because this arm was sampled less.
On this problem, while \MklUCB{} detects the same changes as \GLRklUCB, with larger but comparable delays, it is seen to obtain a larger regret than the two \GLR{} variants, because the tuning of its forced exploration probability makes it explore suboptimal arms more often.

@@

Like for the first problem, we illustrate the behavior of the same four algorithms in Figure~\ref{fig:6:Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb2} above.
In this other problem, the difference between \MklUCB{} and \CUSUMklUCB{} is clear:
the first algorithm fails to detect any change, leading to a large regret,
while the second one detects the changes that happen on the currently optimal arm and some other changes.
Drawing conclusions on their behavior from a single simulation is tricky, as this example of behavior is counter intuitive:
On the one hand, \CUSUM{} uses local restarts, and it should be less efficient than global restarts for this problem, as changes are all global.
On the other hand, \MklUCB{} uses global restarts, but here it fails to detect any changes.
%
The two \GLRklUCB{} variants correctly detect the important changes, and we observe that their delays to detect a change can vary, mainly due to the randomness (we remind that we illustrate only one repetition of the simulation here).
For instance, after the change on arm $1$ (in \textcolor{red}{red}), the \emph{local restart} detects it at time $t=2376$ and the \emph{global restart} detects it at time $t=2701$.

@@

% - Pb 6 is Yahoo! example from Figure~3 in CUSUM-UCB paper \cite{LiuLeeShroff17}
\textbf{Problem 5.}
%
Like problem $3$, this harder problem is also inspired from synthetic data obtained from a real-world database of clicks from \emph{Yahoo!}, but from another competitor paper, see Figure~3 from \cite{LiuLeeShroff17}.
%
It is much harder, with $\Upsilon=81$ change-points on $K=5$ arms for a longer horizon of $T=100000$.
Some arms change at almost every time steps, for a total number of breakpoints $C=179$, but the optimal arm is almost always the same one (\textcolor{red}{arm $0$, with $\bullet$}).
It is a good benchmark to see if the actively adaptive policies do not detect \emph{too many changes}, as the Oracle-Restart policy suffers higher regret in comparison to \klUCB.
Means are also bounded in $[0.01, 0.07]$, with small gaps of amplitude in $[0.001, 0.02]$,
as shown in Figure~\ref{fig:6:Problem_6}.

>>>>

Figure~\ref{fig:6:Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb1} above displays the locations of the successively detected change-points by four algorithms,
$1)$ \MklUCB,
$2)$ \CUSUMklUCB,
$3)$ \GLRklUCB{} with \emph{local restart},
$4)$ \GLRklUCB{} with \emph{global restart}.
In this ``easy'' problem, all algorithms correctly detect the important changes, except \CUSUM{} which detected a change on arm $1$ (\textcolor{red}{in red}) twice after the change-point located at $t=3000$.
The three other algorithms have a very small delay, for instance only $9$ samples from arm $0$ (\textcolor{blue}{in blue}) after its change at time $t=2000$ are enough for the \GLR{} test to detect a change.
Very small delays are possible only after having collected a lot of samples of the arm which changed, and for instance the same algorithm obtains a delay of $32$ samples from \textcolor{red}{arm $1$} for the next change at $t=3000$, because this arm was sampled less.
On this problem, while \MklUCB{} detects the same changes as \GLRklUCB, with larger but comparable delays, it is seen to obtain a larger regret than the two \GLR{} variants, because the tuning of its forced exploration probability makes it explore suboptimal arms more often.

@@

Like for the first problem, we illustrate the behavior of the same four algorithms in Figure~\ref{fig:6:Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb2} above.
In this other problem, the difference between \MklUCB{} and \CUSUMklUCB{} is clear:
the first algorithm fails to detect any change, leading to a large regret,
while the second one detects the changes that happen on the currently optimal arm and some other changes.
Drawing conclusions on their behavior from a single simulation is tricky, as this example of behavior is counter intuitive:
On the one hand, \CUSUM{} uses local restarts, and it should be less efficient than global restarts for this problem, as changes are all global.
On the other hand, \MklUCB{} uses global restarts, but here it fails to detect any changes.
%
The two \GLRklUCB{} variants correctly detect the important changes, and we observe that their delays to detect a change can vary, mainly due to the randomness (we remind that we illustrate only one repetition of the simulation here).
For instance, after the change on arm $1$ (\textcolor{red}{in red}), the \emph{local restart} detects it at time $t=2376$ and the \emph{global restart} detects it at time $t=2701$.

@@

% - Pb 6 is Yahoo! example from Figure~3 in CUSUM-UCB paper \cite{LiuLeeShroff17}
\textbf{Problem 5.}
%
Like problem $3$, this harder problem is inspired from synthetic data obtained from a real-world database of clicks from \emph{Yahoo!}, but from another competitor paper, see Figure~3 from \cite{LiuLeeShroff17}.
%
It is much harder, with $\Upsilon=81$ change-points on $K=5$ arms for a longer horizon of $T=100000$.
Some arms change at almost every time steps, for a total number of breakpoints $C=179$, but the optimal arm is almost always the same one (\textcolor{red}{arm $0$, with $\bullet$}).
It is a good benchmark to see if the actively adaptive policies do not detect \emph{too many changes}, as the Oracle-Restart policy suffers higher regret in comparison to \klUCB.
Means are also bounded in $[0.01, 0.07]$, with small gaps of amplitude in $[0.001, 0.02]$,
as shown in Figure~\ref{fig:6:Problem_6}.
